SeedLing: Building and using a seed corpus \\ for the Human Language Project

### 2014-04-27 docs/computEL-final/paper.tex
added author information

\title{SeedLing: Building and using a seed corpus \\ for the Human Language Project}
%Getting the Ball Rolling: Producing a Foundation Text for a Universal Corpus of the World's Languages}

% \author{Liling Tan, Guy Emerson, Susanne Fertmann, Alexis Palmer and Michaela Regneri \\
%   Universität des Saarlandes \\
%   Campus, 66123 Saarbrücken, Germany \\
%   {\tt liling.tan@uni-saarland.de, emerson@coli.uni-saarland.de,} \\
%   {\tt susfert@coli.uni-saarland.de}}

>>>>

\title{SeedLing: Building and using a seed corpus \\ for the Human Language Project}

\author{Guy Emerson, Liling Tan, Susanne Fertmann, Alexis Palmer and Michaela Regneri \\
Universität des Saarlandes \\
Campus, 66123 Saarbrücken, Germany \\
{\tt liling.tan@uni-saarland.de, emerson@coli.uni-saarland.de,} \\
{\tt susfert@coli.uni-saarland.de, apalmer@coli.uni-sb.de,}\\
{\tt regneri@coli.uni-saarland.de}}
